Phenology and Mycorrhizae Manuscript

### 2023-02-06 manuscriptCode_phenologyAndMycorrhizae.Rmd
Plotting NEON met data
Combining NEON data

#Load Functions and Variables
```{r}
source('sharedVariables.R')
source('NEON_Data_DownloadAndProcess.R')
```

@@

downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
combineNEONdata_PhenoObs(saveType=="bySite") #Saved in individual files by site because 1 file was too large 
combineNEONdata_PhenoObs(saveType=="firstOfPhenophase")
combineNEONdata_PhenoObs(saveType = "allOfPhenophase")
```

#Single Air Temperature At Various Heights 
```{r,eval=FALSE}
dataName="NEON_SingleAirTemperature"
NEON_ID='DP1.00002.001'
selectColumns <- c('horizontalPosition','verticalPosition','tempSingleMean','tempSingleExpUncert','finalQF')
inFileName <- "SAAT_30min.csv"
varName <- 'tempSingleMean'

downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath)
for(funName in c("mean","max","min")){
  calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=mean,funName=funName)
  #Calculate LRs
  gapFillFromDayMet_verticalProfiles(dataName=dataName,dataPath=dataPath,varName=varName,funName=funName)
}

@@

#Precipitation
```{r,eval=FALSE}
dataName="NEON_PrecipitationData"
NEON_ID='DP1.00006.001'
selectColumns <- c('precipBulk','precipExpUncert','precipQF')
inFileName <- c("PRIPRE_30min.csv","SECPRE_30min.csv")
varName <- "precipBulk"

downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath)
calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=sum)
gapFillFromDaymet(dataName=dataName,dataPath=dataPath,varName=varName)

@@

downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath)
funType=mean
funName="mean"
calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)

@@

downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)

@@

#Download NEON Soil Microbe Data
```{r,eval=FALSE}
dataName="NEON_SoilMicrobeComposition"
NEON_ID='DP1.10081.001'
#selectColumns <-
inFileName <- c("mcc_soilSeqVariantMetadata_16S.csv","mcc_soilSeqVariantMetadata_ITS.csv")
#varName <-

downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID) #Note: I had to modify this function to remove the indices for sites that didn't seem to have data. 
combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath)
```

#Download NEON Soil Physical and Chemical Properties
```{r,eval=FALSE}
dataName <- "NEON_soilProperties"
NEON_ID <- "DP1.10086.001"
if(!file.exists(paste0(dataPath,"/",dataName))){
  dir.create(paste0(dataPath,"/",dataName))
}

downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)

dat1 <- dat1 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>%
  group_by(siteID,collectDate,plotID,decimalLatitude,decimalLongitude,elevation,horizon) %>% 
  summarise(soilTemp=mean(soilTemp),litterDepth=mean(litterDepth))

dat2 <- dat2 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>% group_by(siteID,collectDate,plotID,horizon) %>%
  summarise(soilInWaterpH=mean(soilInWaterpH),soilInWaterpH=mean(soilInWaterpH))

allDat <- full_join(dat1,dat2,by=c('siteID','collectDate','plotID','horizon'))

inFileName <- "sls_soilMoisture.csv"
selectColumns <- c('plotID','horizon','soilMoisture','dryMassFraction')
dat3 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
dat3 <- dat3 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d"))%>% group_by(siteID,collectDate,plotID,horizon) %>%
  summarise(soilMoisture=mean(soilMoisture),dryMassFraction=mean(dryMassFraction)) 
allDat <- full_join(allDat,dat3,by=c('siteID','collectDate','plotID','horizon'))

@@

downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID,andStack=FALSE) #missing 30

@@

@@

downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID) #missing 30

@@

dat1 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
                       selectColumns=selectColumns, inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
dat1 <- dat1 %>% mutate(density=dryMass/sampleVolume,
                        somDensity=somDryMass/sampleVolume) %>%
  dplyr::select(-c(sampleVolume,dryMass,somDryMass)) %>%
  group_by(siteID,collectDate,plotID) %>% summarise(densityMean=mean(density),somDensityMean=mean(somDensity))

@@

dat2 <- dat2 %>% group_by(siteID,collectDate,plotID) %>%
  summarise(litterDepth=mean(litterDepth))

allDat <- full_join(dat1,dat2,by=c('siteID','collectDate','plotID'))

@@

dat3 <- dat3 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>%
  filter(cnIsotopeQF=="OK",cnPercentQF=="OK") %>%
  group_by(siteID,collectDate,plotID) %>% summarise(d15N=mean(d15N),
                                                    d13C=mean(d13C),
                                                    nitrogenPercent=
                                                      mean(nitrogenPercent),
                                                    carbonPercent=
                                                      mean(carbonPercent),
                                                    CNratio=
                                                      mean(CNratio))

allDat <- full_join(allDat,dat3,by=c('siteID','collectDate','plotID'))

@@

dat4 <- dat4 %>% group_by(siteID,collectDate,plotID) %>%
  summarise(rootDryMass=mean(rootDryMass),
            mycorrhizaeVisiblePercent=mean(as.numeric(mycorrhizaeVisible),na.rm=TRUE))

allDat <- full_join(allDat,dat4,by=c('siteID','collectDate','plotID'))
outFileName <- paste0(dataName,"ALLdata.csv")
write.csv(file=paste0(dataPath,outFileName),allDat,row.names = FALSE,quote=FALSE)
```

#NEON Plant Structural Characteristics
```{r}

@@

dat1 <- dat1 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>%
  group_by(siteID,collectDate,plotID,plotType,setDate) %>%
  summarise(d15N=mean(d15N), d13C=mean(d13C),nitrogenPercent=mean(nitrogenPercent),
            carbonPercent=mean(carbonPercent), CNratio=mean(CNratio))

@@

dat2 <- dat2 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>%
  group_by(siteID,collectDate,plotID,setDate) %>%
  summarise(ligninPercent=mean(ligninPercent),
            cellulosePercent=mean(cellulosePercent))

allDat <- full_join(dat1,dat2,by=c('siteID','plotID','setDate'))

@@

dat3 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
                        selectColumns=selectColumns, inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
dat3 <- dat3 %>%
  group_by(siteID,collectDate,plotID,setDate,functionalGroup) %>%
  summarise(dryMass=mean(dryMass))

allDat <- full_join(allDat,dat3,by=c('siteID','plotID','setDate'))

@@

downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID) #missing 30

@@

inFileName <- "cfc_chlorophyll.csv"
# selectColumns <- c('plotID','chlCarotWavelength1'),'chlCarotWavelength2',
#                    'chlCarotWavelength3','chlCarotWavelength4',
#                    'chlCarotWavelength1Abs','chlCarotWavelength2Abs',
#                    'chlCarotWavelength3Abs','chlCarotWavelength4Abs',
#                    'extractChlAConc','extractChlBConc')
selectColumns <- c('plotID','extractChlAConc','extractChlBConc','extractCarotConc','sampleID')

@@

allDat <- full_join(dat1,dat2,by=c('siteID','collectDate','sampleID','plotType'))
allDat <- full_join(allDat,dat3,by=c('siteID','collectDate','sampleID','plotID'))
allDat <- full_join(allDat,dat4,by=c('siteID','collectDate','sampleID','plotID'))
allDat <- full_join(allDat,dat5,by=c('siteID','collectDate','sampleID','plotID','plotType'))
##
allDat <- full_join(dat2,dat3,by=c('siteID','plotID','collectDate','sampleID'))
allDat <- full_join(allDat,dat4,by=c('siteID','plotID','collectDate','sampleID'))
allDat <- full_join(allDat,dat5,by=c('siteID','plotID','collectDate','sampleID','plotType'))
allDat <- full_join(allDat,dat1,by=c('siteID','collectDate','sampleID','plotType'))

allDat <- allDat %>% dplyr::select(-sampleID) %>%
  mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>%
  group_by(siteID,collectDate,plotID,plotType) %>%
  summarise(percentGreen=mean(percentGreen),leafMassPerArea=mean(leafMassPerArea),
            dryMassFraction=mean(dryMassFraction),
            d15N=mean(d15N),
            d13C=mean(d13C),
            nitrogenPercent=mean(nitrogenPercent),
            carbonPercent=mean(carbonPercent),
            CNratio=mean(CNratio),
            extractChlAConc=mean(extractChlAConc),
            extractChlBConc=mean(extractChlBConc),
            extractCarotConc=mean(extractCarotConc),
            foliarPhosphorusConc=mean(foliarPhosphorusConc),
            foliarPotassiumConc=mean(foliarPotassiumConc),
            foliarMagnesiumConc=mean(foliarMagnesiumConc),
            foliarSulfurConc=mean(foliarSulfurConc),
            foliarManganeseConc=mean(foliarManganeseConc),
            foliarIronConc=mean(foliarIronConc),
            foliarCopperConc=mean(foliarCopperConc),
            foliarBoronConc=mean(foliarBoronConc),
            foliarZincConc=mean(foliarZincConc),
            ligninPercent=mean(ligninPercent),
            cellulosePercent=cellulosePercent)

>>>>

#Load Functions and Variables
```{r}
source('sharedVariables.R')
source('NEON_Data_DownloadAndProcess.R')
downloadData=FALSE #Change to true if you need to download data 
```

@@

if(downloadData){
downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
}
combineNEONdata_PhenoObs(saveType=="bySite") #Saved in individual files by site because 1 file was too large 
combineNEONdata_PhenoObs(saveType=="firstOfPhenophase")
combineNEONdata_PhenoObs(saveType = "allOfPhenophase")
```

#Single Air Temperature At Various Heights 
```{r,eval=FALSE}
dataName="NEON_SingleAirTemperature"
NEON_ID='DP1.00002.001'
selectColumns <- c('horizontalPosition','verticalPosition','tempSingleMean','tempSingleExpUncert','finalQF')
inFileName <- "SAAT_30min.csv"
varName <- 'tempSingleMean'
if(downloadData){
downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
}
combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath)
for(funName in c("mean","max","min")){
  calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=mean,funName=funName)
  #Calculate LRs
  gapFillFromDayMet_verticalProfiles(dataName=dataName,dataPath=dataPath,varName=varName,funName=funName)
}

@@

#NEON Precipitation
```{r,eval=FALSE}
dataName="NEON_PrecipitationData"
NEON_ID='DP1.00006.001'
selectColumns <- c('precipBulk','precipExpUncert','precipQF')
inFileName <- c("PRIPRE_30min.csv","SECPRE_30min.csv")
varName <- "precipBulk"
if(downloadData){
downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
}
combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath)
calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=sum)

gapFillFromDaymet(dataName=dataName,dataPath=dataPath,varName=varName)

@@

if(downloadData){
downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
}
combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath)
funType=mean
funName="mean"
calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)

@@

if(downloadData){
downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
}

@@

@@

if(downloadData){
downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID,andStack=FALSE) #missing 30 
}

@@

#Download NEON Soil Microbe Data
```{r,eval=FALSE}
dataName="NEON_SoilMicrobeComposition"
NEON_ID='DP1.10081.001'
#selectColumns <-
inFileName <- c("mcc_soilSeqVariantMetadata_16S.csv","mcc_soilSeqVariantMetadata_ITS.csv")
#varName <- 
if(downloadData){
downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID) #Note: I had to modify this function to remove the indices for sites that didn't seem to have data. 
}
combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath)
```

#Download NEON Soil Physical and Chemical Properties
```{r,eval=FALSE}
dataName <- "NEON_soilProperties"
NEON_ID <- "DP1.10086.001"
if(!file.exists(paste0(dataPath,"/",dataName))){
  dir.create(paste0(dataPath,"/",dataName))
}
if(downloadData){
downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
}

dat1 <- dat1 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>% 
  mutate(year=lubridate::year(collectDate)) %>%
  group_by(siteID,year,decimalLatitude,decimalLongitude,elevation,horizon) %>% 
  summarise(soilTemp=mean(soilTemp),litterDepth=mean(litterDepth))

dat2 <- dat2 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>% 
  mutate(year=lubridate::year(collectDate)) %>% group_by(siteID,year,horizon) %>%
  summarise(soilInWaterpH=mean(soilInWaterpH),soilInWaterpH=mean(soilInWaterpH))

allDat <- full_join(dat1,dat2,by=c('siteID','year','horizon'))

inFileName <- "sls_soilMoisture.csv"
selectColumns <- c('plotID','horizon','soilMoisture','dryMassFraction')
dat3 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
dat3 <- dat3 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>% 
  mutate(year=lubridate::year(collectDate)) %>% group_by(siteID,year,horizon) %>%
  summarise(soilMoisture=mean(soilMoisture),dryMassFraction=mean(dryMassFraction)) 
allDat <- full_join(allDat,dat3,by=c('siteID','year','horizon'))

@@

if(!file.exists(paste0(dataPath,"/",dataName))){
  dir.create(paste0(dataPath,"/",dataName))
}
if(downloadData){
downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID) #missing 30 
}

@@

dat1 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
                       selectColumns=selectColumns, inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
dat1 <- dat1 %>% mutate(density=dryMass/sampleVolume,
                        somDensity=somDryMass/sampleVolume) %>%
  dplyr::select(-c(sampleVolume,dryMass,somDryMass)) %>% 
  mutate(year=lubridate::year(collectDate)) %>%
  group_by(siteID,year) %>% summarise(densityMean=mean(density),somDensityMean=mean(somDensity))

@@

dat2 <- dat2  %>% 
  mutate(year=lubridate::year(collectDate)) %>% group_by(siteID,year) %>%
  summarise(litterDepth=mean(litterDepth))

allDat <- full_join(dat1,dat2,by=c('siteID','year'))

@@

dat3 <- dat3 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d"))%>% 
  mutate(year=lubridate::year(collectDate)) %>%
  filter(cnIsotopeQF=="OK",cnPercentQF=="OK") %>%
  group_by(siteID,year) %>% summarise(d15N=mean(d15N),
                                                    d13C=mean(d13C),
                                                    nitrogenPercent=
                                                      mean(nitrogenPercent),
                                                    carbonPercent=
                                                      mean(carbonPercent),
                                                    CNratio=
                                                      mean(CNratio))

allDat <- full_join(allDat,dat3,by=c('siteID','year'))

@@

dat4 <- dat4 %>% 
  mutate(year=lubridate::year(collectDate)) %>% group_by(siteID,year) %>%
  summarise(rootDryMass=mean(rootDryMass),
            mycorrhizaeVisiblePercent=mean(as.numeric(mycorrhizaeVisible),na.rm=TRUE))

allDat <- full_join(allDat,dat4,by=c('siteID','year'))

#NEON Plant Structural Characteristics
```{r}
dataName="NEON_vegetation_structure"
NEON_ID="DP1.10098.001"

if(!file.exists(paste0(dataPath,"/",dataName))){
  dir.create(paste0(dataPath,"/",dataName))
}
if(downloadData){
downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID,includedSeq=42:47) #No: 2, 18,26, 38, 41
}

inFileName <- 'vst_apparentindividual.csv'
selectColumns <- c('plotID','individualID','growthForm','plantStatus',
                   'stemDiameter','measurementHeight','height',
                   'baseCrownHeight','maxCrownDiameter','canopyPosition')
dat1 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
                        selectColumns=selectColumns, inFileName=inFileName,
                        dataPath=dataPath, saveFile = FALSE)
dat1 <- dat1 %>% mutate(year=lubridate::year(date)) %>% dplyr::select(-date)

inFileName <- 'vst_non-woody.csv'
selectColumns <- c('plotID','individualID','growthForm','plantStatus',
                   'stemDiameter','measurementHeight','height',
                   'baseCrownHeight','maxCrownDiameter','canopyPosition',
                   'scientificName')
dat2 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
                        selectColumns=selectColumns, inFileName=inFileName,
                        dataPath=dataPath, saveFile = FALSE)
dat2 <- dat2 %>% mutate(year=lubridate::year(date)) %>% dplyr::select(-date)

inFileName <- 'vst_mappingandtagging.csv'
selectColumns <- c('plotID','individualID','scientificName')
dat3 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
                        selectColumns=selectColumns, inFileName=inFileName,
                        dataPath=dataPath, saveFile = FALSE)
dat3 <- dat3 %>% mutate(year=lubridate::year(date)) %>% dplyr::select(-date)
allDat <- full_join(dat2,dat3,by=c('siteID','year','individualID','scientificName'))

allDat <- full_join(allDat,dat1,by=c('siteID','year','individualID',
                                   'growthForm','plantStatus',
                                   'stemDiameter','measurementHeight','height',
                                   'baseCrownHeight','maxCrownDiameter','canopyPosition'))
outFileName <- paste0(dataName,"ALLdata.csv")
write.csv(file=paste0(dataPath,outFileName),allDat,row.names = FALSE,quote=FALSE)

@@

dat1 <- dat1 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>%
  mutate(year=lubridate::year(collectDate)) %>%
  group_by(siteID,year,plotType,setDate) %>%
  summarise(d15N=mean(d15N), d13C=mean(d13C),nitrogenPercent=mean(nitrogenPercent),
            carbonPercent=mean(carbonPercent), CNratio=mean(CNratio))

@@

dat2 <- dat2 %>% mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>%
  mutate(year=lubridate::year(collectDate)) %>%
  group_by(siteID,year,setDate) %>%
  summarise(ligninPercent=mean(ligninPercent),
            cellulosePercent=mean(cellulosePercent))

allDat <- full_join(dat1,dat2,by=c('siteID','year'))

@@

dat3 <- combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,
                        selectColumns=selectColumns, inFileName=inFileName,dataPath=dataPath,saveFile = FALSE)
dat3 <- dat3 %>%
  mutate(year=lubridate::year(collectDate)) %>%
  group_by(siteID,year,setDate,functionalGroup) %>%
  summarise(dryMass=mean(dryMass))

allDat <- full_join(allDat,dat3,by=c('siteID','year'))

@@

if(downloadData){
downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID) #missing 30 
}

@@

inFileName <- "cfc_chlorophyll.csv"
selectColumns <- c('plotID','extractChlAConc','extractChlBConc','extractCarotConc','sampleID')

@@

allDat <- full_join(dat2,dat3,by=c('siteID','plotID','collectDate','sampleID'))
allDat <- full_join(allDat,dat4,by=c('siteID','plotID','collectDate','sampleID'))
allDat <- full_join(allDat,dat5,by=c('siteID','plotID','collectDate','sampleID','plotType'))
allDat <- full_join(allDat,dat1,by=c('siteID','collectDate','sampleID','plotType'))

allDat <- allDat %>% dplyr::select(-sampleID) %>%
  mutate(collectDate=format(as.POSIXct(collectDate,                                                  format='%Y-%m-%dT%H:%M'),format="%Y-%m-%d")) %>%
  mutate(year=lubridate::year(collectDate)) %>%
  group_by(siteID,year,plotType) %>%
  summarise(percentGreen=mean(percentGreen),leafMassPerArea=mean(leafMassPerArea),
            dryMassFraction=mean(dryMassFraction),
            d15N=mean(d15N),
            d13C=mean(d13C),
            nitrogenPercent=mean(nitrogenPercent),
            carbonPercent=mean(carbonPercent),
            CNratio=mean(CNratio),
            extractChlAConc=mean(extractChlAConc),
            extractChlBConc=mean(extractChlBConc),
            extractCarotConc=mean(extractCarotConc),
            foliarPhosphorusConc=mean(foliarPhosphorusConc),
            foliarPotassiumConc=mean(foliarPotassiumConc),
            foliarMagnesiumConc=mean(foliarMagnesiumConc),
            foliarSulfurConc=mean(foliarSulfurConc),
            foliarManganeseConc=mean(foliarManganeseConc),
            foliarIronConc=mean(foliarIronConc),
            foliarCopperConc=mean(foliarCopperConc),
            foliarBoronConc=mean(foliarBoronConc),
            foliarZincConc=mean(foliarZincConc),
            ligninPercent=mean(ligninPercent),
            cellulosePercent=cellulosePercent)
